---
title: "Place, Values, and Public Opinion About Climate Change in South Carolina"
bibliography: /Users/nowlinmc/Dropbox/refs.bib
csl: /Users/nowlinmc/Dropbox/Projects/Manuscripts/csl/american-political-science-association.csl
output:
  word_document:
    reference_docx: /Users/nowlinmc/Dropbox/Projects/Manuscripts/template.docx
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_knit$set(root.dir = normalizePath(".."))

# code to incorporate comments and changes from Word doc 
# redoc::dedoc("manuscript/sc-climate-change-views.docx", overwrite = TRUE)
```

Introduction
============

In the United States, coastal communities are experiencing ever growing
populations and urban sprawl that outpace inland communities. This is certainly
the case for coastal communities in South Carolina. According to data from the
U.S. Census Bureau, between 2010 and 2019 the population of the Charleston, S.C.
Metro Area grew by 20.7 percent and the Myrtle Beach, S.C. Metro Area grew by
28.3 percent. As the population of coastal communities in South Carolina
continues to grow, more people and infrastructure will be put at risk from
natural hazards that are likely to be exacerbated by climate change
[@neumannFutureCoastalPopulation2015]. Within the last few years, the state of South Carolina
has experienced several major hurricane and flooding events including the
historic flood of 2015, as well as Hurricane's Matthew in 2016, Irma in 2017, and Florence
in 2018.

Despite the clear scientific consensus regarding the anthropogenic causes of and
risks posed by climate change, some in the public are skeptical about the causes
and consequences of climate change. Much of this skepticism is driven by values
such as political beliefs or cultural beliefs.[^1] However, as more individuals,
particularly those in coastal communities, are exposed to climate change
associated risks, will that have an impact on their views of climate change? 
Which matters more for views about climate change, cultural and political beliefs or living in a
coastal community?

Polarization among both elites and the public regarding climate change is driven
in large part by core values, such as political ideology, that inform and guide
the opinions that individuals develop about particular issues. With regard to
complex scientific and technical issues like climate change, opinions may be
based less on the underlying science and more on the particular policy solution
[@campbellSolutionAversionRelation2014]. For example, if climate change requires government
actions or regulations, then conservatives and others that are generally opposed
to government intervention conclude that climate change must not be a problem.
If science is seen as implying particular solutions to problems that run counter
to beliefs, then there is reason to doubt the science.

Core values are implicated in how the public views climate change; however, the
public is, by-and-large, not consistently ideological in terms of conservative
and liberal [see @kinderNeitherLiberalConservative2017]. Yet, this does not necessarily mean that the
mass public lacks an underlying structure of core values [@ripbergerCulturalTheoryMeasurement2014].
One measure of values, cultural theory, drawn from the cultural theory of risk,
has been shown to be a consistent measure of values for those with little
political sophistication [@ripbergerReconsideringRelationshipCultural2012], and for those that are
non-ideological [@jacksonTheoryPreferenceFormation2015].

In this paper, we leverage an original survey of South Carolina residents
collected in 2017 to address questions regarding the influence of *values* ---
specifically those derived from the cultural theory of risk --- and *place* ---
living in a coastal community --- on views about climate change. Specifically,
we asked respondents if they believe climate change is happening and the
certainty of that belief; the level of risks they believe climate change poses;
their level of concern regarding sea-level rise; and their concern regarding
flooding in their local area. Overall, we find that cultural values,
particularly egalitarian worldviews, are the most important influences on
views about climate change and its associated risks. In addition, we find that
values are most strongly related to climate change views when climate change is
explicitly mentioned (i.e., climate change is happening, and the risks posed by
climate change). Place attachments, specifically living in a coastal county, are
more influential with concerns about sea-level rise and flooding than they are
with climate change beliefs. These results point to a values-based
disconnect between concern about climate change generally and place-based
concerns about specific climate change impacts.

Cultural Theory of Risk
=======================

The cultural theory of risk, initially developed by Mary Douglas and Aaron
Wildavsky [@douglasRiskCultureEssay1982], posits that risk
perceptions are formed based on the ways in which preferred societal structures
and relationships could be threatened. As noted by @wildavskyTheoriesRiskPerception1990,
"Among all possible risks, those selected for worry or dismissal are functional
in the sense that they strengthen one of these ways of life and weaken the
others" (44). Structures and relationships in society are grounded in two
dimensions that include a *grid* dimension that proscribes various rules and
roles that structure society and a *group* dimension that proscribes the
relationships between the individual and the community. On the grid dimension,
the characterization of high-grid refers to individuals who prefer more rigid
social structures with defined rules for engaging with others, while low grid
refers to more *laissez-faire* structures where individuals are free to manage
social relations on their own. For the group dimension, the characterization of
high-group refers to individuals who are highly connected and cohesive, while
low-group refers to individuals who are more individualized and independent.

When combined, the grid and group dimensions produce four ways-of-life that act
as guideposts for an idealized social structure. The ways-of-life form the basis
of four cultural worldviews including hierarchy, egalitarian, individualist, and
fatalist. Figure 1 shows the placement of each cultural worldview on the grid
and group dimensions. Understanding these four cultural worldviews can provide
insights about how individuals perceive risks across a variety of domains
[@tanseyCulturalTheoryRisk1999; @johnsonCulturalTheoryContributions2020].

**Figure 1: about here**

Starting with the hierarchical worldview, hierarchs are associated with being
high on both the grid and group dimensions. Hierarchical individuals place
emphasis on maintaining the status quo of the "natural order" of society and are
averse to social disruptions, demonstrations, and crime which have the potential
to threaten this order. They also tend to trust expert knowledge, often
accepting risks as long as the risk is justified by reputable individuals or
groups, such as government or subject experts.

The egalitarian worldview is associated with the low-grid and high-group
dimensions. Individuals with this characteristic are skeptical towards expert
knowledge due to perceived potential for misuse of authority and are likely to
support actions that promote social equality. Egalitarians also oppose
destructive human intervention with nature (i.e., development, deforestation),
because they view nature as fragile and vulnerable. Egalitarians are likely to
be opposed to increasing environmental risks due to the fear of potentially
causing irreversible damage to the ecosystem and promoting actions which
increase the likelihood of placing negative conditions on the future of society.
In sum, those who fall within the egalitarian worldview are likely to have
heightened concerns regarding social and environmental risks.

Individualistic worldviews are associated with the low-grid, low-group
dimensions. At the center of this worldview is the concern for freedom and
opposition towards any action which may obstruct, limit, or remove individual
rights. Individualists accept risks as potential opportunities with the
exception that those risks do not have a negative impact on individual rights.
Individualists often oppose actions such as warfare and installation of
socialist governments, viewing them as controls on individual freedoms. They are
likely to align with market-based economic practices, including free trade,
minimal government intervention in markets, and accumulation of individual
wealth. Individualists starkly contrast the egalitarians perception of nature,
viewing nature as highly resilient to human intervention and causing them to be
less concerned with human treatment of nature. Individualists are likely to have
minimal concern for environmental risks.

Fatalistic cultural worldviews fit within the high-grid, low-group dimensions.
Generally, fatalists are not concerned with risk due to their perceived lack of
authority or agency to mitigate them. Because they feel constrained by societal
norms, fatalists will feel indifferent about risks and view risks as mostly
brought about and decided upon by others. Since fatalists have the perception
that they lack the agency to mitigate risks, they often strive to distance
themselves from learning about risks due to their unavoidable nature. From this
viewpoint, nature also does not provide any clues to the moral status of human
interventions, accepting that nature is chaotic, and individuals must solve
problems with nature as they present themselves. Those who align closely with a
fatalist worldview are likely to have minimal concern for risks in general,
hinging on the lack of perceived capability to mitigate risks themselves.

Cultural theory has been applied extensively in the energy and environmental policy
domains, given that risk and perceptions of risk are entangled in decisions
about energy production and use as well as environmental and natural resource
management. For example, what are the risks associated with nuclear technology
versus the benefit of a low-carbon energy source? What are the risks of climate
change on the natural environment versus the risks of regulation of energy
production? The worldviews exemplified by the cultural theory of risk inform how
individuals evaluate such risks and weigh risk trade-offs. Indeed, cultural
worldviews have been shown to be predictive of attitudes regarding a host of
energy and environmental issues including the New Ecological Paradigm (NEP)
scale [@nowlinEnvironmentalPolicymakingEra2019], climate change
[@jonesLeadingWayCompromise2011; @kahanPolarizingImpactScience2012; @nowlinCulturalTheoryPartisanship2020], weather perceptions
[@goebbertWeatherClimateWorldviews2012], nuclear energy
[@vandegraaffUnderstandingNuclearControversy2016], nuclear waste [@jenkins-smithModelingStigmaEmpirical2001], hydraulic
fracturing [@boudetFrackingControversyCommunication2014], power lines [@moyerUnderstandingLocalPolicy2016], and
renewable energy [@tumlisonWhatExplainsLocal2018; @westRenewableEnergyPolicy2010].[^2]

In general, on environmental issues, such as climate change, the largest divide
exists between egalitarians and individualists [@grendstadCulturalTheoryPostmaterialism1997].
Egalitarians tend to more concerned than other cultural types about risks to the
natural environment that threaten collective well-being and are seen as a
by-product of individualistic over-consumption. For individualists, the threat
posed to private enterprise and individual autonomy by government action is seen
as greater than the risks associated with potential environmental degradation
that government action would lessen or prevent. As a result, egalitarians tend
to more concerned about climate change than individualists, whereas,
individualists tend to be more supportive of fossil-fuel energy production than
egalitarians. Hierarchs tend to be split on environmentalism and environmental
concern broadly (Nowlin 2019), yet hierarchs do tend to think that climate
change is happening, is anthropogenic, and poses both personal and sociotropic
risks [@jonesLeadingWayCompromise2011; @nowlinCulturalTheoryPartisanship2020]. Finally, fatalists view nature, along with all
other facets of life, as impervious to human control, therefore, they tend to
not to be concerned about environmental issues. Given the nature of the fatalist
worldview, we do not pose any hypotheses about how fatalists view climate
change.

In the subsequent analysis, we examine whether respondents believe that climate
change is happening and whether it poses risks. Our risk measures include
perceived risk from climate change generally as well as concern about two
specific effects of climate change; sea-level rise and flooding. Based on
previous work, we posit the following hypotheses:

H1: Increasing hierarchy will be associated with *increasing* certainty that
climate change is happening and poses risks

H2: Increasing egalitarianism will be associated with *increasing* certainty
that climate change is happening and poses risks

H3: Increasing individualism will be associated with *decreasing* certainty that
climate change is happening and poses risks

Geographic Location and 'Sense of Place'
========================================

Cultural worldviews provide a values-based framework for individuals to assess
risk. Namely, activities or events that threaten the preferred social ordering
are those that pose the greatest risk. However, exposure to potential hazards
can vary across temporal and spatial scales, meaning that geographic location is
likely to play a key role in determining an individual's perception of risk. To
this point, it is important to consider the immediacy of risk and proximity to
which the individuals are located to said risk. Living in close proximity to
certain natural environments has the potential for individuals to perceive risks
to these areas as greater than those who are more distantly located. For
example, those that live inland are not as likely to perceive climate change as
a serious risk compared to individuals living in coastal communities that are
likely to experience some of its immediate impacts [@brodyExaminingRelationshipPhysical2008; @hamiltonEnvironmentalViewsCoast2015; @monteroSocialPerceptionCoastal2020].
Indeed, several studies have found place effects with regard to perceptions of
climate and environmental issues. In a study examining residents in rural
communities, @hamiltonPlaceEffectsEnvironmental2010 found that county level unemployment and
population growth were significant predictors of environmental views,
controlling for demographics and political beliefs. Those that live in areas
with increasing populations were more concerned about the impacts of sprawl and
more likely to support environmental regulations that restrict development. In
addition, @goebbertWeatherClimateWorldviews2012 found that individuals were able to correctly
identify whether their local area had experienced increased flooding and drought
over time, but did not recognize the increase in seasonal temperatures. They found that 
perceived temperature increases were driven by cultural worldviews. Finally,
@bhattachanLinkingResidentialSaltwater2019 found that residents in areas most vulnerable to
saltwater intrusion were more likely than residents less at risk to view
intrusion as risky. These studies point to respondents being attuned to risks in
their geographic areas and, therefore, risk perceptions aren't only
values-based, but place-based as well.

While geography certainly plays a role in determining an individual's perception
of risk, the length of residence in these areas, either at the individual or
generational level, may also impact the perception of risk. Drawing on one
example, residents in subtropical, temperate regions like South Carolina may not
perceive the impact of climate change as immediately and personally as Alaskan
residents. Residents of Alaska are experiencing rapid erosion and changing soil structure, caused 
by permafrost thawing over time, due to
rising temperatures. Likewise, Alaskan residents and researchers may also
perceive the impacts of melting permafrost differently than the indigenous
Alaskan peoples who have extensive knowledge of the landscape to which they
maintain their spiritual and ancestral ties [@watsonTransgressionsManMoon2014]. In this
context, sense of place can ultimately influence how an individual perceives
risks.

Sense of place is also a factor within South Carolina coastal communities.
@halfacreNostalgiaCatalystConservation2016 noted that sense of place in the lowcountry,
characterized by feelings of nostalgia, act as a catalyst for conservation
efforts for culturally significant areas in the region. She further noted how
nostalgia from lived experiences has cultivated liberal environmental views in
individuals living within a predominantly conservative region. Ethnographic
evidence of coastal South Carolina residents, developed by Halfacre (2016),
suggest sense of place plays a role in determining someone's perception of the
environment, and likely their perception of risks relating to said environment.
Additional work has shown a connection between place-based nostalgia and 
conservation in other parts of the US [@seamanConservingNostalgiaExploring2019]. 
Investigating the connections between
geography, sense of place, and environmental concerns can provide further
evidence to understand individual and community perceptions of risks associated
with impacts to and from nature.

Previous work has shown that residents develop a sense of place about where they
live based on lived experiences and risk exposure that inform their views on
issues like climate change. Therefore, we posit the following hypothesis:

H4: Living in a coastal area will be associated with *increasing* certainty that
climate change is happening and poses risks

In the next section we describe the data and variables used to test our
hypotheses.

**Data and Variables**

```{r load data, include=FALSE, message=FALSE}
SCstate <- read.csv("data/SCimpute.csv", stringsAsFactors=TRUE)
library(tidyverse)
library(broom)
library(sjmisc)
library(survey)
```

```{r descriptive, include=FALSE, message=FALSE}
hierA <- psy::cronbach(data.frame(SCstate$hier1,SCstate$hier2,SCstate$hier3))
egalA <- psy::cronbach(data.frame(SCstate$egal1,SCstate$egal2,SCstate$egal3))
indivA <- psy::cronbach(data.frame(SCstate$indiv1,SCstate$indiv2,SCstate$indiv3))
fatalA <- psy::cronbach(data.frame(SCstate$fatal1,SCstate$fatal2,SCstate$fatal3))
```

The data for the following analysis comes from an original survey given to
`r nrow(SCstate)` respondents from the state of South Carolina.[^3]
Respondents came from a sample purchased from
Survey Sampling International (SSI). The survey was administered through
Qualtrics and was fielded in August 2017. In terms of demographics, the median
age of our sample is `r round(median(SCstate$age))` , which
matches the median age according to US Census estimates.[^4]. In our sample,
`r round(mean(SCstate$male),2)*100` percent of the respondents identified as male and
`r round(mean(1-SCstate$male),2)*100` percent identified as female. Our sample represents a
slightly more female population than the actual population within the state,
which is 51.5 percent female and 48.5 percent male. For our sample,
`r round(mean(SCstate$white),2)*100` percent of the respondents identified as White, higher
than the South Carolina population which is 67.3 percent White. We measured
education attainment on 1 = less than high school to 7 = graduate or
professional degree scale and the mean for the education scale is
`r round(mean(SCstate$edu),2)`, indicating some college to an associate degree, which
is similar to US Census estimates. Finally, for income we use a 1 = 0 to
\$19,999 to 7 = \$150,000 or more scale to measure total family income for 2016.
The mean of the income scale is `r round(mean(SCstate$inc),2)` and that indicates an
average income between \$40,000 to \$79,999, which captures the median income of
\$51,015. Overall, our sample is slightly more female and more White than
the South Carolina population, therefore in the subsequent analysis we weighted
gender and race to match the population.

Climate Change Beliefs
----------------------

Our interest is examining the relationships between values, place, and 
climate change beliefs of South Carolina residents. In the survey, we asked
respondents several climate related questions including whether they think
climate change is happening and, overall a majority of respondents,
`r round(mean(SCstate$gccDummy),2)*100` percent, indicated that they think climate change is
happening. Next we asked respondents, *how sure are you that climate change
\[is/is not\] happening*, with 0 = not at all sure, 1 = somewhat sure, 2 = very
sure, and 3 = extremely sure. Then, we combined the climate change is happening
question and the certainty question to create a climate change certainty scale
that ranges from -3 = extremely sure climate change *is not* happening to 3 =
extremely sure climate change *is* happening. The mean for the climate change
certainty scale is `r round(mean(SCstate$gccCertScale),2)`, which indicates that, on average,
respondents are somewhat to very sure that climate change is happening.

We also asked respondents their perceived level of risk posed by climate change
by asking, *on the scale from 0 to 10, where 0 means no risk and 10 means
extreme risk, how much risk do you think climate change poses for people and the
environment*. The mean for the climate change risk question was
`r round(mean(SCstate$gccrsk),2)`, indicating that, on average, respondents believe that
climate change poses moderate to extreme risks. Finally, using a similar 0 to 10
scale, we asked respondents how concerned they are about *sea-level rise* and
*flooding in their local area*, two issues expected to be exacerbated by climate
change. For sea-level rise concern the mean `r round(mean(SCstate$SLR),2)`, on the 0
to 10 scale and for flooding concern the mean was `r round(mean(SCstate$flooding),2)`,
indicating that respondents are, on average, at least moderately to somewhat
concerned about sea-level rise and flooding.

Cultural Theory Measures
------------------------

To measure cultural worldview, we used the same set of questions used in other
cultural theory research [see @jacksonTheoryPreferenceFormation2015; @jonesLeadingWayCompromise2011; @moyerCulturalPredispositionsSpecific2019; @nowlinCulturalTheoryPartisanship2020; @ripbergerReconsideringRelationshipCultural2012; @tumlisonCulturalValuesTrust2019]. Specifically, we asked
respondents their agreement with 12 statements, three statements for each
cultural type, on a 1 (strongly disagree) to 7 (strongly agree) scale. The
statements were presented in random order. The three statements were then
averaged into a 1 to 7 scale for each cultural type. As shown below, the
Cronbach's $\alpha$ for each cultural worldview scale indicates sufficient
reliability.

For *hierarchs* the three statements are below. The mean of the 1 to 7 hierarch
scale is `r round(mean(SCstate$hier),2)` and the Cronbach's $\alpha$ =
`r round(hierA$alpha,2)`.

-   The best way to get ahead in life is to work hard to do what you are told to
    do

-   Society is in trouble because people do not obey those in authority

-   Society would be much better off if we imposed strict and swift punishment
    on those who break the rules

For *egalitarians* the mean for the scale is `r round(mean(SCstate$egal),2)` and the
Cronbach's $\alpha$ = `r round(egalA$alpha,2)`. The egalitarian questions
include:

-   What society needs is a fairness revolution to make the distribution of
    goods more equal

-   Society works best if power is shared equally

-   It is our responsibility to reduce differences in income between the rich
    and the poor

For *individualists* the mean for the scale is `r round(mean(SCstate$indiv),2)` and the
Cronbach's $\alpha$ = `r round(indivA$alpha,2)`. The questions were:

-   Even if some people are at a disadvantage, it is best for society to let
    people succeed or fail on their own

-   Even the disadvantaged should have to make their own way in the world

-   We are all better off when we compete as individuals

Finally, for *fatalists* the mean for the scale is `r round(mean(SCstate$fatal),2)` and
the Cronbach's $\alpha$ = `r round(fatalA$alpha,2)`. The fatalist questions
include:

-   The most important things that take place in life happen by chance

-   No matter how hard we try, the course of our lives is largely determined by
    forces beyond our control

-   For the most part, succeeding in life is a matter of chance

Apart from cultural worldviews, we also measured political beliefs including
ideology and partisanship. Political beliefs are strongly associated with views
about climate change, with conservatives and Republicans less likely to think
climate change is happening or poses a risk than liberals and Democrats
[@dunlapPoliticalDivideClimate2016; @hamiltonEducationPoliticsOpinions2011; @mccrightPoliticalOrientationModerates2011]. For ideology we asked respondents to place themselves
on a 1 to 7 scale, with 1 = strongly liberal, 4 = middle of the road, and 7 =
strongly conservative. The mean for ideology was `r round(mean(SCstate$ideology),2)`,
which is just between "middle of the road" and slightly conservative. For
partisanship, we combined two questions -- *with which party do you most
identify* and *how strongly do you identify with that party* -- to create a 1 to
7 partisanship scale.[^5] The partisanship scale ranges from 1 = strong
Democrat, 4 = true independent, 7 = strong Republican and the mean of the scale
is `r round(mean(SCstate$partisan),2)`, which indicates an independent to Republican lean.

Measure of Place
----------------

For place we asked respondents whether they lived in one of the coastal counties
in South Carolina including Beaufort, Berkeley, Charleston, Colleton,
Dorchester, Georgetown, Horry, and Jasper. Overall, `r table(SCstate$coastCount)[2]` or
`r round(mean(SCstate$coastCount),2)*100` percent of respondents indicated that were from one of
the eight coastal counties. This is similar to the 27 percent of the population
of South Carolina that is estimated to live in a coastal area.[^6] In addition,
as a control measure we asked respondents how long they have been a resident of
their current county with 1 = less than two years, 2 = 2 to 5 years, 3 = 5 to 10
years, 4 = 10 to 20 years, and 5 = more than 20 years. The average on the 1 to 5
measure was `r round(mean(SCstate$resident),2)`.

Analysis and Results
====================

```{r analysis, include=FALSE, message=FALSE}
## weighted 
dataUnweighted <- svydesign(ids=~1, data=SCstate)
malePop <- data.frame(male = c("0","1"), Freq = nrow(SCstate) * c(0.52, 0.48))
whitePop <- data.frame(white = c("0","1"), Freq = nrow(SCstate) * c(0.33, 0.67))
dataRake <- rake(design = dataUnweighted,
                 sample.margins = list(~male, ~white),
                 population.margins = list(malePop, whitePop))

summary(gccCertModelW <- svyglm(gccCertScale~hier+egal+indiv+fatal+ideology+partisan+coastCount+resident+age+male+white+edu+inc, design=dataRake))
summary(gccRskolsW <- svyglm(gccrsk~hier+egal+indiv+fatal+ideology+partisan+coastCount+resident+age+male+white+edu+inc, design=dataRake))
summary(SLRolsW <- svyglm(SLR~hier+egal+indiv+fatal+ideology+partisan+coastCount+resident+age+male+white+edu+inc, design=dataRake))
summary(floodolsW <- svyglm(flooding~hier+egal+indiv+fatal+ideology+partisan+coastCount+resident+age+male+white+edu+inc, design=dataRake))

stargazer::stargazer(gccCertModelW, gccRskolsW, SLRolsW, floodolsW, type = "html", 
                     title = "Table 1: Regression Estimates of Climate Change Beliefs", align=TRUE, 
                     dep.var.labels = c("Climate Change Certainty","Climate Change Risk", 
                                        "Sea-Level Rise Concern", "Flooding Concern"), 
                     covariate.labels = c("Hierarch", "Egalitarian", "Individualist", "Fatalist", "Ideology (more conservative)", 
                                          "Partisanship (more Republican)", "Coastal County", "Time as Resident","Age","Gender (Male=1)", 
                                          "Race (White=1)","Education","Income"),
                     no.space=TRUE, header=FALSE, out = "manuscript/table1w.doc") 
# plots 
library(ggplot2)
sjPlot::set_theme(base = theme_bw())

gccCertPlotW <- sjPlot::plot_model(gccCertModelW, terms = c("hier", "egal", "indiv", "fatal", "ideology","partisan","coastCount","resident"), 
                                  type = "std", sort.est = TRUE, show.values = TRUE, value.offset = .4, colors = "bw",
                                  title = "Climate Change Certainty", 
                                  axis.labels = c("Individualist", "Ideology", "Partisanship", "Hierarch",  "Fatalist", "Time as Resident", "Coastal County", 
                                                  "Egalitarian")) + ylim(-.75,.75) + xlab("")

gccRskPlotW <- sjPlot::plot_model(gccRskolsW, terms = c("hier", "egal", "indiv", "fatal", "ideology","partisan","coastCount","resident"), 
                                  type = "std", sort.est = TRUE, show.values = TRUE, value.offset = .4, colors = "bw",
                                  title = "Climate Change Risk", 
                                  axis.labels = c("Individualist", "Partisanship",  "Ideology", "Time as Resident", "Hierarch", "Fatalist", "Coastal County", 
                                                  "Egalitarian")) + ylim(-1,1)

gccSLRPlotW <- sjPlot::plot_model(SLRolsW, terms = c("hier", "egal", "indiv", "fatal", "ideology","partisan","coastCount","resident"), 
                                  type = "std", sort.est = TRUE, show.values = TRUE, value.offset = .4, colors = "bw",
                                  title = "Sea-Level Rise Concern", 
                                  axis.labels = c("Partisanship", "Individualist","Fatalist", "Time as Resident", "Ideology", "Hierarch", "Coastal County", 
                                                  "Egalitarian")) + ylim(-1,2)

gccFloodPlotW <- sjPlot::plot_model(floodolsW, terms = c("hier", "egal", "indiv", "fatal", "ideology","partisan","coastCount","resident"), 
                                  type = "std", sort.est = TRUE, show.values = TRUE, value.offset = .4, colors = "bw",
                                  title = "Flooding Concern", 
                                  axis.labels = c("Individualist", "Partisanship", "Ideology", "Time as Resident", "Fatalist", "Hierarch", "Coastal County", 
                                                  "Egalitarian")) + ylim(-1,2.75)

ggsave("fig-output/fig2.png", gridExtra::grid.arrange(gccCertPlotW, gccRskPlotW, nrow = 2))
ggsave("fig-output/fig3.png", gridExtra::grid.arrange(gccSLRPlotW, gccFloodPlotW, nrow = 2))
```

We posited several hypotheses regarding how cultural worldviews and place inform
views about climate change. As noted, we expect increasing hierarchy and
increasing egalitarianism to be associated with increasing certainty that
climate change is happening and that it poses risks (H1 and H2). Conversely, we
expect increasing individualism to be associated with decreasing certainty that
climate change is happening and poses risks (H3). With regard to place, we
expect that living in a coastal county is associated with believing that climate
change is happening, and it poses risks (H4).

To test our hypotheses, we use linear regression to examine the relationship
between climate change beliefs, cultural theory, and place. Specifically, we
examined the certainty that climate change is occurring, the risks posed by
climate change, the concern for sea-level rise, and the concern for flooding as
a function of cultural worldviews and living in a coastal county while
controlling for political beliefs, time as resident, and demographics. The
results are shown in Table 1.[^7]

**Table 1: about here**

Looking first to climate change certainty (column 1), we find, consistent with
H2, that increasing egalitarianism is associated with an increase in certainty
that climate change is happening. Additionally, and as expected (H3), increasing
individualism is associated with decreasing certainty that climate is happening.
However, against expectations increasing hierarchy (H1) and living in a coastal
county (H4) are not associated with climate change certainty. For political
beliefs, increasing conservatism and increasing Republicanism is associated with
a decrease in climate change certainty (at p$<$ 0.10 for partisanship). With
regard to the demographic control variables, older respondents expressed less
certainty that climate is happening than younger respondents. Those with more
education were also more likely than those with less education to think that
climate change is happening (at p$<$ 0.10).

A similar pattern holds for the perceived risks of climate change with regard to
cultural worldviews. As shown in Table 1 column 2, increasing egalitarianism is
associated with an increase in perceived climate change risks (H2), whereas, an
increase in individualism is associated with a decrease in risk perception (H3).
In addition, and as expected, those that live in coastal counties were more
likely to see climate change as a risk than those in other parts of the state,
at p$<$ 0.10 (H4). Conservatives and Republicans were less likely to view
climate change as risky than liberals and Democrats and those with more
education were likely to view it as riskier than those with less education.

Looking to both sea-level rise and flooding concern (columns 3 and 4 in Table
1), we see that increasing egalitarianism is associated with increased concern
for both sea-level rise and flooding (H2). Additionally, increasing hierarchy is
associated with increased concern for flooding at p$<$ 0.10. Also, increasing
Republicanism was associated with a decrease in concern for sea-level rise and
for flooding at p$<$ 0.10. For place, respondents in coastal counties were more
likely to be concerned about sea-level rise and flooding than were respondents
in other parts of South Carolina (H4). Finally, older respondents were less
likely than younger respondents, at p$<$ 0.10, to be concerned about increased
flooding.

Next, we examine the magnitude of the impacts of cultural worldviews,
political beliefs, and place using the standardized regression coefficients
from the models in Table 1.[^8] The standardized regression coefficients
allows us to examine the relative impact of each of the independent variables on the
dependent variable. With this approach, we can see if values or place matter
more for climate change views. Figure 2 shows the standardized regression
coefficients, arranged by size from largest to smallest, for the climate
change certainty model and the climate change risk model. In addition, Figure
2 indicates the statistical significance of each of the standardized
coefficients.

**Figure 2: Standardized Regression Coefficients of Climate Change Beliefs about here**

As shown and looking at the absolute value of the coefficients, the egalitarian
scale has the largest effect on climate change certainty, followed by the
individualist scale and ideology. For climate change risk, egalitarian and
individualist worldviews are significant as are political beliefs. Overall,
egalitarian beliefs have the largest impact on perceived climate change risk,
followed by individualist beliefs, then partisanship, and finally ideology.
Next, we examine the standardized regression coefficients for sea-level rise and
flooding concern, and those results are shown in Figure 3.

**Figure 3: Standardized Regression Coefficients of Sea-Level Rise and Flooding Concern about here**

For sea-level rise concern, egalitarian beliefs had the largest impact, followed
by living in a coastal county and, lastly, partisanship (more Republican). With
regard to flooding, only egalitarianism and living in a coastal county were
significant, with egalitarian beliefs having a larger impact than living in a
coastal county.

Discussion
==========

In this paper, we examined the influence of cultural worldviews and place on
views about climate change in South Carolina. As expected, increasing
egalitarianism was associated with increased certainty that climate change is
happening and an increased perception of risk from climate change, as well as
increasing concern for sea-level rise and flooding. Indeed, egalitarianism was
the strongest predictor of climate change views, as indicated by the
standardized regression results shown in Figures 2 and 3. Additionally,
individualism was associated with decreased certainty that climate change is
happening and decreased perceptions of risk, with individualism being the second
strongest predictor of those views (see Figures 2 and 3). However, there was no
association with individualism and concerns over sea-level rise and flooding.
This seeming disconnect may be because individualists tend to see threats to
individual freedom and economic activity as risks, therefore, they view
government regulations to address climate change as a larger risk than climate
change itself. To date, there has not been as much discussion
of government activities to address sea-level rise and flooding, so these
aspects of climate change have not become as politicized. However, as
governments in coastal communities start to initiate ways to address sea-level
rise and flooding, such as building a large seawall, these efforts may start to
shift the views of individualists. On the other hand, sea-level rise and
flooding do have the potential to disrupt individual and commercial activity,
which could be a concern for individualists. Further research should examine
how individualists view risks associated with the effects of climate change that
may cause economic disruption as well as their views on how governments at all
levels should address those risks.

We also expected that hierarchs would be more likely to believe that climate
change is happening and poses risks; however, we found that increasing hierarchy
was only associated with a slight increase in concerned for flooding. As noted,
previous research has found that hierarchs, perhaps attuned to scientists and
other expert knowledge, tend to believe that climate is happening and presents
risks for individuals and society. Yet, recent work has found a divide between
hierarchs that are politically conservative and those that are politically
liberal on climate change beliefs, with conservative hierarchs not likely to
believe that climate change poses risks [@nowlinCulturalTheoryPartisanship2020]. It is
possible that hierarchs in South Carolina are more politically conservative than
hierarchs in other areas and are, therefore, less likely to think climate change
is happening or a risk. Future research should further
example the ideological interactions with cultural worldviews and how those
interactions might impact views about polarized political issues.

For place impacts, we found that respondents living in a coastal county were
more likely than those in other parts of the state to view climate change as a
risk (at p $<$ 0.10) and to be concerned about sea-level rise and flooding. This
was as expected given that those in coastal communities are, in many ways, on
the "front lines" of climate change and likely to experience many of its effects
such as sea-level rise and the resulting increased storm surges and increased
flooding first-hand. Interestingly, those in coastal counties were no more
likely to be certain that climate change is happening even as they were more
likely to see it and its effects as cause for concern. It is possible that 
coastal residents recognized changes within the landscape caused by climate
change related impacts, but do not prescribe to climate change as a reality or
associate it with the observable impacts. This is perhaps because of the politicized nature of the term "climate change"
compared to the lived experiences of increased flooding. Finally, living in a
coastal county was second only to increasing egalitarianism as a predictor of
concern for sea-level rise and flooding. Once again, this is likely because of
the experiences of those living in coastal communities. Our measures of place
are at the county level and, therefore, are relatively rough. More precise
measures, perhaps distance from the coast, would give a better sense of how
place impacts climate change views. Future research should try and obtain more
precise measures of location and compare those to cultural wordlviews and
political beliefs.

Conclusion
==========

Over the last few years the state of South Carolina has experienced several
major flooding events that were likely exacerbated by climate change. These
types of events are likely to intensify in the coming years. Despite the risks,
as well as the strong scientific consensus regarding the causes and consequences
of climate change, many do not think climate change is happening or that it is a
matter of concern. In this paper, we examined both values and place as possible
explanations for how residents of South Carolina view climate change.

Overall, we find that values, particularly egalitarian worldviews, are the most
consistent and significant predictor of climate change beliefs. The impacts of
egalitarianism on climate change beliefs are larger than those of place, even
though residents living in coastal communities are likely to face greater risks
from climate change than those in other parts of the state. Yet, place effects
are important, with those living in coastal counties more concerned about
sea-level rise and flooding in their areas. However, our findings point to the
value-based divide over climate change and this divide is likely to impede
progress on mitigation and adaptation responses to climate change at all levels
of government in the US.

\newpage

References
==========

\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}
\vspace*{-0.2in}
\singlespace
\noindent


[^1]: By cultural beliefs, we are referring to the ways-of-life derived from
    cultural theory.

[^2]: In addition, cultural worldviews are associated with various myths of
    nature regarding how resilient nature is to human interference (see
    Thompson, Ellis, and Wildavsky 1990; Nowlin 2019; Price, Walker, and
    Boschetti 2014)

[^3]: We imputed missing data using the Amelia package (version 1.7.6) in R. For
    more information see: <http://gking.harvard.edu/amelia/>

[^4]: US Census data available here:
    <https://www.census.gov/acs/www/data/data-tables-and-tools/data-profiles/>

[^5]: Independents were asked to which party do they most lean and were recoded.

[^6]: See here: <https://coast.noaa.gov/states/south-carolina.html>

[^7]: As indicated, we added weights to gender and race so that our sample would
    more closely match the population. For the analysis, we used the survey
    package (version 4.0) in R to weight and estimate the models.

[^8]: Note, we do not include control variables in the figures; however, they
    are controlled for in the models shown.
